cardinalR: Generating interesting high-dimensional data structures

### 2025-06-24 paper-cardinalR.Rmd
Try to reduce the number of pages

```{r, label = "fig-expbranches-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `expbranches` data."}
#| fig-width: 15
#| fig-height: 5

expbranches_proj1 + expbranches_proj2 + expbranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-linearbranches-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `linearbranches` data."}
#| fig-width: 15
#| fig-height: 5

linearbranches_proj1 + linearbranches_proj2 + linearbranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-curvybranches-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvybranches` data."}
#| fig-width: 15
#| fig-height: 5

curvybranches_proj1 + curvybranches_proj2 + curvybranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-orglinearbranches-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `orglinearbranches` data."}
#| fig-width: 15
#| fig-height: 5

orglinearbranches_proj1 + orglinearbranches_proj2 + orglinearbranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-orgcurvybranches-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `orgcurvybranches` data."}
#| fig-width: 15
#| fig-height: 5

orgcurvybranches_proj1 + orgcurvybranches_proj2 + orgcurvybranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-gridcube-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gridcube` data."}
#| fig-width: 15
#| fig-height: 5

gridcube_proj1 + gridcube_proj2 + gridcube_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-unifcube-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `unifcube` data."}
#| fig-width: 15
#| fig-height: 5

unifcube_proj1 + unifcube_proj2 + unifcube_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-cubehole-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `cubehole` data."}
#| fig-width: 15
#| fig-height: 5

cubehole_proj1 + cubehole_proj2 + cubehole_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-cubic-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `quadratic` and `cubic` data."}
#| fig-width: 15
#| fig-height: 10

@@

```{r, label = "fig-pyrrect-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrrect` data."}
#| fig-width: 15
#| fig-height: 5

pyrrect_proj1 + pyrrect_proj2 + pyrrect_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-pyrtri-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrtri` data."}
#| fig-width: 15
#| fig-height: 5

pyrtri_proj1 + pyrtri_proj2 + pyrtri_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-pyrstar-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrstar` data."}
#| fig-width: 15
#| fig-height: 5

pyrstar_proj1 + pyrstar_proj2 + pyrstar_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-pyrholes-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrholes` data."}
#| fig-width: 15
#| fig-height: 5

pyrholes_proj1 + pyrholes_proj2 + pyrholes_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-scurve-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `scurve` and `scurvehole` data."}
#| fig-width: 15
#| fig-height: 10

@@

```{r, label = "fig-circle-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `circle` data."}
#| fig-width: 15
#| fig-height: 5

circle_proj1 + circle_proj2 + circle_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-curvycycle-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvycycle` data."}
#| fig-width: 15
#| fig-height: 5

curvycycle_proj1 + curvycycle_proj2 + curvycycle_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-unifsphere-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `unifsphere` data."}
#| fig-width: 15
#| fig-height: 5

unifsphere_proj1 + unifsphere_proj2 + unifsphere_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-gridedsphere-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gridedsphere` data."}
#| fig-width: 15
#| fig-height: 5

gridedsphere_proj1 + gridedsphere_proj2 + gridedsphere_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-clusteredspheres-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `clusteredspheres` data."}
#| fig-width: 15
#| fig-height: 5

clusteredspheres_proj1 + clusteredspheres_proj2 + clusteredspheres_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-hemisphere-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `hemisphere` data."}
#| fig-width: 15
#| fig-height: 5

hemisphere_proj1 + hemisphere_proj2 + hemisphere_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-crescent-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `crescent` data."}
#| fig-width: 15
#| fig-height: 5

crescent_proj1 + crescent_proj2 + crescent_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-curvycylinder-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvycylinder` data."}
#| fig-width: 15
#| fig-height: 5

curvycylinder_proj1 + curvycylinder_proj2 + curvycylinder_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-sphericalspiral-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `sphericalspiral` data."}
#| fig-width: 15
#| fig-height: 5

sphericalspiral_proj1 + sphericalspiral_proj2 + sphericalspiral_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-helicalspiral-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `helicalspiral` data."}
#| fig-width: 15
#| fig-height: 5

helicalspiral_proj1 + helicalspiral_proj2 + helicalspiral_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-conicspiral-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `conicspiral` data."}
#| fig-width: 15
#| fig-height: 5

conicspiral_proj1 + conicspiral_proj2 + conicspiral_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-nonlinear-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `nonlinear` data."}
#| fig-width: 15
#| fig-height: 5

nonlinear_proj1 + nonlinear_proj2 + nonlinear_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

>>>>

@@

@@

@@

@@

```{r, label = "fig-orgcurvybranches-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `expbranches`, `linearbranches`, `curvybranches`, `orglinearbranches`, `orgcurvybranches` data.", fig.width=15, fig.height=25}

expbranches_proj1 + expbranches_proj2 + expbranches_proj3 +
linearbranches_proj1 + linearbranches_proj2 + linearbranches_proj3 +
curvybranches_proj1 + curvybranches_proj2 + curvybranches_proj3 +
orglinearbranches_proj1 + orglinearbranches_proj2 + orglinearbranches_proj3 +
orgcurvybranches_proj1 + orgcurvybranches_proj2 + orgcurvybranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

@@

@@

```{r, label = "fig-cubehole-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gridcube`, `unifcube`, and `cubehole` data.", fig.width=15, fig.height=15}

gridcube_proj1 + gridcube_proj2 + gridcube_proj3 +
unifcube_proj1 + unifcube_proj2 + unifcube_proj3 +
cubehole_proj1 + cubehole_proj2 + cubehole_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-cubic-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `quadratic` and `cubic` data.", fig.width=15, fig.height=10}

@@

@@

@@

@@

```{r, label = "fig-pyrholes-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrrect`, `pyrtri`, `pyrstar`, and `pyrholes` data.", fig.width=15, fig.height=20}

pyrrect_proj1 + pyrrect_proj2 + pyrrect_proj3 +
pyrtri_proj1 + pyrtri_proj2 + pyrtri_proj3 +
pyrstar_proj1 + pyrstar_proj2 + pyrstar_proj3 +
pyrholes_proj1 + pyrholes_proj2 + pyrholes_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-scurve-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `scurve` and `scurvehole` data.", fig.width=15, fig.height=10}

@@

@@

@@

@@

@@

@@

```{r, label = "fig-hemisphere-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `circle`, `curvycycle`, `unifsphere`, `gridedsphere`, `clusteredspheres`, and `hemisphere` data.", fig.width=15, fig.height=35, out.width="80%", fig.align='center'}

circle_proj1 + circle_proj2 + circle_proj3 +
curvycycle_proj1 + curvycycle_proj2 + curvycycle_proj3 +
unifsphere_proj1 + unifsphere_proj2 + unifsphere_proj3 +
gridedsphere_proj1 + gridedsphere_proj2 + gridedsphere_proj3 +
clusteredspheres_proj1 + clusteredspheres_proj2 + clusteredspheres_proj3 +
hemisphere_proj1 + hemisphere_proj2 + hemisphere_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

@@

@@

@@

@@

@@

```{r, label = "fig-triginometric-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `crescent`, `curvycylinder`, `sphericalspiral`, `helicalspiral`, `conicspiral`, and `nonlinear` data.", fig.width=15, fig.height=35, out.width="80%", fig.align='center'}

crescent_proj1 + crescent_proj2 + crescent_proj3 +
curvycylinder_proj1 + curvycylinder_proj2 + curvycylinder_proj3 +
sphericalspiral_proj1 + sphericalspiral_proj2 + sphericalspiral_proj3 +
helicalspiral_proj1 + helicalspiral_proj2 + helicalspiral_proj3 +
conicspiral_proj1 + conicspiral_proj2 + conicspiral_proj3 +
nonlinear_proj1 + nonlinear_proj2 + nonlinear_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

### 2025-06-24 paper-cardinalR.tex
Try to reduce the number of pages

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-expbranches-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `expbranches` data.}\label{fig:fig-expbranches-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-linearbranches-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `linearbranches` data.}\label{fig:fig-linearbranches-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-curvybranches-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `curvybranches` data.}\label{fig:fig-curvybranches-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-orglinearbranches-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `orglinearbranches` data.}\label{fig:fig-orglinearbranches-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-orgcurvybranches-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `orgcurvybranches` data.}\label{fig:fig-orgcurvybranches-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-gridcube-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `gridcube` data.}\label{fig:fig-gridcube-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-unifcube-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `unifcube` data.}\label{fig:fig-unifcube-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-cubehole-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `cubehole` data.}\label{fig:fig-cubehole-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-pyrrect-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `pyrrect` data.}\label{fig:fig-pyrrect-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-pyrtri-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `pyrtri` data.}\label{fig:fig-pyrtri-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-pyrstar-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `pyrstar` data.}\label{fig:fig-pyrstar-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-pyrholes-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `pyrholes` data.}\label{fig:fig-pyrholes-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-circle-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `circle` data.}\label{fig:fig-circle-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-curvycycle-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `curvycycle` data.}\label{fig:fig-curvycycle-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-unifsphere-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `unifsphere` data.}\label{fig:fig-unifsphere-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-gridedsphere-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `gridedsphere` data.}\label{fig:fig-gridedsphere-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-clusteredspheres-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `clusteredspheres` data.}\label{fig:fig-clusteredspheres-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-hemisphere-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `hemisphere` data.}\label{fig:fig-hemisphere-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-crescent-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `crescent` data.}\label{fig:fig-crescent-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-curvycylinder-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `curvycylinder` data.}\label{fig:fig-curvycylinder-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-sphericalspiral-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `sphericalspiral` data.}\label{fig:fig-sphericalspiral-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-helicalspiral-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `helicalspiral` data.}\label{fig:fig-helicalspiral-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-conicspiral-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `conicspiral` data.}\label{fig:fig-conicspiral-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-nonlinear-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `nonlinear` data.}\label{fig:fig-nonlinear-proj}
\end{figure}

>>>>

@@

@@

@@

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-orgcurvybranches-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `expbranches`, `linearbranches`, `curvybranches`, `orglinearbranches`, `orgcurvybranches` data.}\label{fig:fig-orgcurvybranches-proj}
\end{figure}

@@

@@

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-cubehole-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `gridcube`, `unifcube`, and `cubehole` data.}\label{fig:fig-cubehole-proj}
\end{figure}

@@

@@

@@

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-pyrholes-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `pyrrect`, `pyrtri`, `pyrstar`, and `pyrholes` data.}\label{fig:fig-pyrholes-proj}
\end{figure}

@@

@@

@@

@@

@@

@@

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{paper-cardinalR_files/figure-latex/fig-hemisphere-proj-1}

}

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `circle`, `curvycycle`, `unifsphere`, `gridedsphere`, `clusteredspheres`, and `hemisphere` data.}\label{fig:fig-hemisphere-proj}
\end{figure}

@@

@@

@@

@@

@@

@@

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{paper-cardinalR_files/figure-latex/fig-triginometric-proj-1}

}

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `crescent`, `curvycylinder`, `sphericalspiral`, `helicalspiral`, `conicspiral`, and `nonlinear` data.}\label{fig:fig-triginometric-proj}
\end{figure}
